Exercise: South German Credit

### 2020-07-02 pkg/partykit/inst/ULGcourse-2020/exercises/exercise_german_credit.Rmd
small corrections in section 'aggregation'; added section on distributional forests
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3035 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: c8e5510b3c8d99b30497ac311a8f39e92a900e30

>>>>

```{r, include = FALSE}
library("ranger")
rf <- ranger(formula, data = train, num.trees = 20)
rf$confusion.matrix
rf <- ranger(formula, data = train, num.trees = 500)
rf$confusion.matrix

cf <- cforest(formula, data = na.omit(train), ntree = 20)

pred_cf <- predict(cf, newdata = test)
pred_rf <- predict(rf, data = test)
```
